Visualize ukb whole genome, s40.22

### 2020-11-20 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
block feature

* qq plot for SNPs
```{r qqsnp, fig.height= 5, fig.width=5}
gg_qqplot(b$PVALUE) +
  theme_bw(base_size = 24) +
  theme(
    axis.ticks = element_line(size = 0.5),
    panel.grid = element_blank()
    # panel.grid = element_line(size = 0.5, color = "grey80")
  )
```

@@

  # df$ifcausal <- mapvalues(df$ifcausal, from=c(0,1), to=c("Non causal", "Causal"))

  df$ifcausal <- mapvalues(df$ifcausal, from=c(0,1),to=c("darkgreen", "salmon"))

  plot(df$TWAS.p, df$pip, col = df$ifcausal, main = main, xlab = "-log10(TWAS p value)", ylab = "PIP")
  # fig <- plot_ly(data = df, x = ~ TWAS.p, y = ~ pip, color = ~ ifcausal,
  #                colors = c( "salmon", "darkgreen"), type ="scatter", text = ~ paste("Name: ", paste0(runtag,":",name),
  #                                                                  "\nChr: ", chr,  "\nPos:", pos))

>>>>

* qq plot for SNPs
```{r qqsnp, fig.height= 5, fig.width=5}
gg_qqplot(b$PVALUE) +
  theme_bw(base_size = 24) +
  theme(
    axis.ticks = element_line(size = 0.5),
    panel.grid = element_blank()
    # panel.grid = element_line(size = 0.5, color = "grey80")
  )
```
# Block features

```{r block}

a <- read.table(paste0(outputdir, "20201001-1-1.config9.gene.nofilter.r.txt"), header =T)
b <-  read.table(paste0(outputdir, "20201001-2-1.config9.gene.nofilter.r.txt"), header =T)
m1 <- read.table(paste0(outputdir, "20201001-1-1.config9.nofilter.r.txt"), header =T)
m2 <- read.table(paste0(outputdir, "20201001-2-1.config9.nofilter.r.txt"), header =T)

hist(a$p1-a$p0, main = NULL, xlab = "Block size(bp)", col = "salmon")

par(mfrow=c(2,2))
hist(a$nCausal, xlab = "No.causal genes", col = "salmon", breaks=100, xlim=c(0,15), main ="low power")
hist(b$nCausal, xlab = "No.causal genes", col = "salmon", breaks=100, xlim=c(0,15), main ="high power")
hist(m1$nCausal, xlab = "No.causal genes + SNPs", col = "salmon", breaks=100, xlim=c(0,15), main ="low power")
hist(m2$nCausal, xlab = "No.causal genes + SNPs", col = "salmon", breaks=100, xlim=c(0,15), main ="high power")
```

@@

  # df$ifcausal <- mapvalues(df$ifcausal, from=c(0,1),to=c("darkgreen", "salmon"))
  # plot(df$TWAS.p, df$pip, col = df$ifcausal, main = main, xlab = "-log10(TWAS p value)", ylab = "PIP")
  # 
  df$ifcausal <- mapvalues(df$ifcausal, from=c(0,1), to=c("Non causal", "Causal"))
  fig <- plot_ly(data = df, x = ~ TWAS.p, y = ~ pip, color = ~ ifcausal,
                 colors = c( "salmon", "darkgreen"), type ="scatter", text = ~ paste("Name: ", paste0(runtag,":",name),
                                                                   "\nChr: ", chr,  "\nPos:", pos))

### 2020-11-20 analysis/simulation-susieI-ukbWG-gtex.adipose_visual.Rmd
pip cali
block feature

plot_all <- function(SERf, phenof, chrom, ldres = NULL){
  a <- fread(SERf , header =T)
  load(phenof)

@@

```{r sim 2-1-1, out.width = "98%", out.height="95%"}
chrom <- 1
tag <- "20201001-2-1"
pipfile <-  paste0(outputdir, tag, ".config.1.SERI.txt")
phenof <- paste0(simdatadir, "simu_", tag, "-pheno.Rd")
plot_all(pipfile, phenof, chrom)
```

>>>>

plot_all <- function(SERf, phenof, chrom, ldres = NULL){
  a <- fread(SERf, header =T)
  load(phenof)

@@

```{r sim 1-3-17, out.width = "98%", out.height="95%"}
chrom <- 13
tag <- "20201001-1-2"
pipfile <-  paste0(outputdir, tag, ".config6.SERI.txt")
phenof <- paste0(simdatadir, "simu_", tag, "-pheno.Rd")
plot_all(pipfile, phenof, chrom)
```
